{\helveticaitalic{Supplementary Material}}

### 2022-03-30 tex/sections/results.tex
Pre-submission

\subsection{Mathematical analysis of two-cell network}
\label{sec:assumptions}
% Summary of assumptions
The goal of the following mathematical analysis is to reduce the complexity of the
eight-dimensional system to a more tractable problem.
As we will explain, we do this by approximating the full dynamics by a reduced system describing the dynamics of the depression variable $d$ of either of the two cells.
We will construct the solution of $d$ in a piecewise manner from one spike to the next, first during the active phase, and then during the silent phase.
This construction will require two assumptions about the membrane and synaptic dynamics.
The first assumption states that during a burst the active cell fires at its uncoupled period $T$, which simplifies the construction of the solution of $d$.
The second assumption states that once the inhibitory conductance acting on the silent cell drops below a critical threshold, the cell is immediately released and fires.
The second assumption is necessary to predict the release time of the silent cell, which allows us to model the recovery of $d$ during the silent phase.
In other words, the second assumption requires that the release of the silent cell from inhibition depends only on the timecourse of the inhibition, and not on the membrane dynamics of the silent cell.
The approximate validity of both assumptions can be observed in coupled relaxation-oscillator types of neurons such as the Morris-Lecar model we use, and will be numerically verified below.
Both assumptions were first used in~\cite{bose2011} to derive algebraic conditions that guarantee the periodicity of the depression variable for different $n:n$ solutions.
However here we will use these assumptions to construct a Poincaré map of $d$, which will provide a geometric intuition for the dynamics of the full two-cell network and its dependence on model parameters.

% Assumption 1: active phase
\linelabel{line:E1}
Our first assumption about the model states that the active cell fires at its uncoupled period $T$, that is, during the active phase of a burst we have $ISI=T$.
Solution profiles in \cref{fig:burst-sols} suggest that the $ISI$s are indeed approximately constant.
Numerically computing $ISI$s for all stable $n:n$ solutions in \cref{fig:bif-diagram} reveals that $ISI$s differ by at most $1\, \si{ms}$ from the intrinsic firing period $T\approx 376\, \si{ms}$.
Assuming $ISI=T$ seems reasonable given that inhibition acting on the silent cell decays exponentially on a much shorter timescale $\tau_{\kappa}$ than the duration of the $ISI$. Therefore once the silent cell is released its trajectory quickly approaches the spiking limit cycle.
Naturally the above assumption requires a sufficiently small $\tau_{\kappa}$, and fails when $\tau_{\kappa}$ is large.
In the Supplementary Material \cref{sec:tauk} we numerically explore how different values of $\tau_{\kappa}$ affect the $ISIs$ of the active cell.
Finally, assuming $ISI=T$ allows us to ignore the non-linear membrane dynamics during the active phase, and to construct the evolution of the synaptic variables iteratively from spike to spike.
\linelabel{line:E2}

% Assumption 2: Release
\linelabel{line:release1}
Our second assumption states that the silent cell is released and spikes as soon as the total inhibitory conductance $\bar g s$ acting on it drops below some threshold value.
We call this critical threshold value the ``release conductance'', and define it as the value of $\bar g s$ at the time when the voltage of the quiet cell first crosses the firing threshold $v_{\theta}$, that is when that cell is released and fires its first spike.
Recall that when a cell is quiet its $v$- and $w$-nullclines intersect at a stable fixed point and $\bar g s > g_{bif}$.
% The following does not necessarily imply that it fires instantly on release.
A sufficient condition for the quiet cell to be released is therefore $\bar g s < g_{bif}$.
However, depending on the topology of the stable manifold, the $(v,w)$-trajectory of the silent cell can escape the stable fixed point and allow the cell to produce a spike for $\bar g s > g_{bif}$.
In this case the value of the release conductance depends on the type of $n:n$ solution and the coupling strength $\bar g$.
For any stable $n:n$ solution in \cref{fig:bif-diagram} we can compute an associated release conductance numerically by recording the value of $\bar g s$ at the time of the first spike of the silent cell.
% ''Converges'' is probably the wrong word here...
Such values of the release conductance are shown in \cref{fig:gstar-diag}A, and the graph suggests that as $n$ increases, the value of the release conductance converges to some constant conductance value $g^{\star} \approx 0.0068\, \si{mS/cm^2}$.
Here $g^{\star}$ is the value of $\bar g s$ at the end of a cycle of a suppressed solution, just before the active cell spikes.
Using $g^{\star}$ as a constant approximation for the release conductance will allow us to formulate a scalar condition that predicts the release time of the silent cell.
Moreover, using $g^{\star}$ is convenient because its exact value can be derived explicitly, as will be shown in the following section.

Assuming a constant release conductance for all $n:n$ solutions will naturally introduce some error in the prediction of the release time of the silent cell.
We can compute that error for any associated solution in \cref{fig:gstar-diag}A by calculating the time interval between the first spike of the silent cell and the time when $\bar g s$ first crosses $g^{\star}$.
We will call this time interval the ``release delay''.
\Cref{fig:gstar-diag}B shows the numerically computed graph of such release delays.
For $n>1$ the absolute delays are smaller than $2\, \si{ms}$.
Therefore, using
\begin{equation}
	~\label{eq:release}
	\bar g s=g^{\star}
\end{equation}
as a constant release condition for all $n:n$ solutions allows us to accurately predict the timing of the release of the quiet cell.
And to simplify the terminology, from now on we will refer to \cref{eq:release} simply as the ``release condition''.
\linelabel{line:release2}

% NOTE: Perhaps mention the first assumption here as well.
In summary: We assume that the release condition is sufficient to predict when the silent cell is released.
Due to the symmetry of $n:n$ solutions the release occurs at exactly half the period of the full cycle, that is at $P/2$.
The release time therefore uniquely determines the type of $n:n$ solution.
Furthermore, computation of the release time does not depend on the membrane nor the synaptic dynamics of the silent cell.
Instead, the solution of the synaptic variable $s$ of the active cell is sufficient to predict when $\bar g s =g^{\star}$ is satisfied.
\linelabel{line:F}
Finally, the value of $s$ at each spike time is determined by the evolution of the depression variable $d$ of the active cell.
Constructing a solution of $d$ during the active phase of either cell will therefore uniquely determine the solution of the full eight-dimensional network.
However, finding the solution $d$ requires us to know the initial value $d(0)$ at the start of a cycle at $t=0$.
In the next section we will construct a scalar return map that tracks these initial values $d(0)$ from cycle to cycle of stable $n:n$ solutions.

\subsection{Construction of the scalar Poincaré map}
In this section we construct the scalar Poincaré map $\Pi_n:d^{\star}\mapsto d^{\star}$.
Here the discrete variable $d^{\star}$ tracks the values of the continuous depression variable $d$ at the beginning of each $n:n$ burst.
The map $\Pi_{n}$ therefore describes the evolution of $d$, of either of the two cells, from the beginning of one cycle to the beginning of the next cycle.
To simplify the map construction we will assume that an active cell fires exactly $n$ times before it becomes silent.
We will construct $\Pi_n$ by evolving $d$ first during the active phase and then during the silent phase of the $n:n$ limit cycle.
The terms ``active'' and ``silent'' phases will be defined in terms of the state of the depression variable.
Hence, during the active phase the depression variable of the active cell will both decay and recover, while during the silent phase it will only recover.
First, let us give explicit definitions of the active and silent phases of a burst.
A schematic illustration of both phases is given in \cref{fig:free-quiet}.

Suppose that at $t=0$ cell 1 becomes active with some initial $d(0)$. Cell 1 then fires $n$ spikes at the uncoupled period $T=T_{a}+T_{s}$.
Let $s(t)$ and $d(t)$ be the corresponding solutions of the synaptic and depression variables of cell 1.
After $n$ spikes the total conductance $\bar g s(t)$ acting on the silent cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}.
That is at some time $t=(n-1)T + T_{a} + \Delta t$, where $\Delta t < T_{s}$ will be determined below, we have $\bar g s(t)=g^{\star}$ \citep{bose2011}.
Cell 2 is then released and prevents cell 1 from further spiking.
Once released, cell 2 also fires $n$ spikes until cell 1 becomes active once again.
Let $P_n$ denote the full cycle period of a $n:n$ solution:
\begin{equation}
	~\label{eq:P}
	P_n = 2\Big( (n-1)T + T_{a} + \Delta t \Big).
\end{equation}
We can now define the active and silent phases of cell 1 explicitly.
The active phase of a burst is the interval that lasts from the first spike time up until the beginning of the silent phase of the last spike, that is for time $0<t<(n-1)T + T_{a}$.
During the active phase of cell 1, the silent cell 2 is inhibited sufficiently strong to prevent it from firing, hence $\bar g s > g^{\star}$.
The silent phase of cell 1 is the remaining duration of the cycle when the cell is not firing, that is for $(n-1)T + T_{a} < t < P_n$.
Hence the silent phase lasts for $(n-1)T + T_{a} + 2\Delta t$.

@@

Given constant $T_{a}$ and $T_{s}$, parameter $\lambda$ determines how much the synapses depresses during the active phase of the spike, while $\rho$ determines how much it recovers during the silent phase.
Since $0<\lambda, \rho<1$, the map in \cref{eq:map-d} is increasing and contracting, with a fixed point at
\begin{equation}
	~\label{eq:dsup}
	d_{s}=\frac{1-\rho}{1-\lambda\rho},
\end{equation}
where $0<d_{s}<1$.
The value $d_{s}$ is the maximum depression value that can be observed in the suppressed solution where the active cell fires at its uncoupled period $T$ (see \cref{fig:burst-sols}E).
Using the release condition in \cref{eq:release} allows us to derive the value of the minimum coupling strength that will produce the full suppressed solution, denoted as $\bar g_{s}$.
% TODO  Would be good to elaborate on the idea that lambda and tau can be viewed as the new time constants in the reduced system.
Solving \cref{eq:dot-s-down} for $s(t)$ with $t=T_{s}$ and setting the initial value $s(0)=d_s\lambda$ then gives us the aforementioned approximation of the release conductance $g^{\star}$:
\begin{equation}
	\label{eq:gstar}
	\bar g_s d_s\lambda e^{-T_{s}/\tau_\kappa}=g^{\star} \approx 0.0068\, \si{mS/cm^2}.
\end{equation}
By substituting the definition of $d_{s}$ in \eqref{eq:dsup} and rearranging, we can also write $\bar g_s$ as a function of $\lambda$ and $\rho$:
\begin{equation}
	\label{eq:gs}
	\bar g_s(\lambda, \rho) = \frac{1/\lambda-\rho}{1-\rho} e^{T_{s}/\tau_\kappa}g^\star.
\end{equation}
Note that the above dependence of $\bar g_{s}$ on $\lambda$ is linear and monotonically decreasing.
Increasing $\lambda$ reduces the strength of the depression of the active cell.
This in turn allows the active cell to fully suppress the silent cell at smaller values of $\bar g$.

Solving \cref{eq:map-d} gives us the linear map $\delta_n$, that for some initial $d^\star$ computes the depression at the $n$th spike time, that is $d(t_n)$:
\begin{equation}
	\label{eq:delta-map}
	\delta_n(d^\star) = (\lambda \rho)^{n-1} d^\star + (1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^i.
\end{equation}
Since $\lambda < 1$, function $\delta_n$ is a linearly increasing function of $d^\star$ with a fixed point at $d_s$ for all $n$.
Having identified $d$ after $n$ spikes, we can now use the release condition $\bar g s = g^{\star}$ (\cref{eq:release}) to find $\Delta t$.
At the last ($n$th) spike of the active phase at time $t_n = (n-1)T$ the synapse variable $s$ is set to the respective value of $d(t_n) = \delta_n(d^\star)$, and mirrors the value of $d$ for the duration of $T_{a}$.
At the end of the active phase at time $t_n + T_{a}$ variable $d$ has decayed to $\delta_n(d^\star) \lambda$, therefore
\begin{equation}
	s(t_n + T_{a})=\delta_n(d^\star)\lambda.
\end{equation}
Finally $s$ decays exponentially for $\Delta t < T_{s}$.
Solving \cref{eq:dot-s-down} with initial condition $s(0)=\dn(d^\star)\lambda$ yields:
\begin{equation}
	~\label{eq:s-sol}
	s(\Delta t)=\dn(d^\star) \lambda e^{-\Delta t/\tau_\kappa}.
\end{equation}
Substituting $s(\Delta t)$ into $s$ of the release condition (\cref{eq:release}) gives then
\begin{equation}
	~\label{eq:release2}
	\bar g \dn(d^\star) \lambda e^{-\Delta t/\tau_\kappa}=g^{\star}.
\end{equation}
Our assumption of the release condition guarantees that the silent cell 2 spikes and becomes active when $\bar g s - g^{\star}$ crosses zero.
Solving \cref{eq:release2} for $\Delta t$ allows us to compute $\Delta t$ as a function of $d^{\star}$, which defines our map $F_{n}$:
\begin{equation}
	\label{eq:Fn-map}
	F_n(d^\star):=\tau_\kappa \ln{\left(\frac{\bar g }{g^\star} \lambda \delta_{n}(d^\star)\right)}= \Delta t.
\end{equation}

@@

\Cref{eq:g} also allows us to find the critical fixed point connected with the fold bifurcation, namely $\big(d^\star_b(n), \bar g_b(n)\big)$, which is the global minimum
of $G_n(d^\star_f)$:
\begin{align}
	d^\star_b(n) & = \operatorname{argmin} G_n(d^\star_f), \\
	\bar g_b(n)  & = \min{G_n(d^\star_f)}.
\end{align}
Function $G_n$ is strictly monotonic on the respective intervals of $d^\star_f$ that correspond to the stable and unstable fixed points, that is
\begin{align}
	\dv{G_n}{d^\star_f} & < 0, \text{ for } d^\star_f>d^\star_b(n) \text{ stable},   \\[0.5ex]
	\dv{G_n}{d^\star_f} & > 0, \text{ for } d^\star_f<d^\star_b(n) \text{ unstable},
\end{align}
which allows us to express the stable and unstable fixed points as the inverse of $G_n$ on their respective intervals of $d^\star_f$.
Because we are primarily interested in the stable fixed points $d^\star_f>d^\star_b(n)$, we define the stable fixed point function $d^\star_f = \phi_n(\bar g)$ as
\begin{equation}
	\label{eq:phi}
	\phi_n(\bar g):= G_n^{-1}(\bar g).
\end{equation}
Function $\phi_n(\bar g)$ is also monotonic, and is therefore straightforward to compute numerically.
Here we use the Python package Pynverse \citep{pynverse} for that purpose.

@@

% TODO: Edit a bit more
\Cref{fig:final-bif} shows the period $P_{n}(\bar g)$ as predicted by the fixed points of $\Pi_{n}$ (\cref{eq:period}) plotted on their respective intervals $\bar g \in [\bar g_{\mathcal{L}}(n),\bar g_{\mathcal{R}}(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
Here $g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ were computed from \cref{eq:L,eq:R}, respectively.
Note that the width of $n:n$ branches decreases with $n$, which confirms the inequality in \cref{eq:robustness}.
That is, bursts with more spikes occur on increasingly smaller intervals of $\bar g$, which can be interpreted as a lost of robustness with respect to the coupling strength of long-cyclic solutions.
We also note the occurrence of bistability between pairs of $n:n$ and $(n+1):(n+1)$ branches, which also confirms our initial observation in
\cref{eq:coexistence}.
As previously observed in \cref{fig:folds}B our maps prediction of the cycle period is accurate.
However, the mismatch in the left and right branch borders is significant.
This mismatch might be due to the millisecond release delay error (\cref{fig:gstar-diag}B) induced by our assumption of a constant release conductance for all $n:n$ solutions (see \cref{eq:release}).
Another explanation for the border mismatch could be that our assumptions on the time scales of $w$ and $s$ dynamics do not hold near the stability borders, and that they can only be captured by more complex approximations.
Nevertheless, our map allows approximate extrapolation of the cycle period and the respective bifurcation borders where numerical integration of the ODEs would require a very small time step.

>>>>

\subsection{Mathematical analysis of two-cell network}
\label{sec:assumptions}
% Summary of assumptions
The goal of the following mathematical analysis is to reduce the complexity of the
eight-dimensional system to a more tractable problem.
As we will explain, we do this by approximating the full dynamics by a reduced system that describes the evolution of the depression variable $d$ of either of the two cells.
We will construct the solution of $d$ in a piecewise manner from one spike to the next, first during the active phase, and then during the silent phase.
This construction will require two assumptions about the membrane and synaptic dynamics.
The first assumption states that during a burst the active cell fires at its uncoupled period $T$, which simplifies the construction of the solution of $d$.
The second assumption states that once the inhibitory conductance acting on the silent cell drops below a critical threshold, the cell is immediately released and fires.
The second assumption is necessary to predict the release time of the silent cell, which allows us to model the recovery of $d$ during the silent phase.
In other words, the second assumption requires that the release of the silent cell from inhibition depends only on the timecourse of the inhibition, and not on the membrane dynamics of the silent cell.
The approximate validity of both assumptions can be observed in coupled relaxation-oscillator types of neurons such as the Morris-Lecar model we use, and will be numerically verified below.
Both assumptions were first used in~\cite{bose2011} to derive algebraic conditions that guarantee the periodicity of the depression variable for different $n:n$ solutions.
However here we will use these assumptions to construct a Poincaré map of $d$, which will provide a geometric intuition for the dynamics of the full two-cell network and its dependence on model parameters.

% Assumption 1: active phase
\linelabel{line:E1}
Our first assumption about the model states that the active cell fires at its uncoupled period $T$, that is, during the active phase of a burst we have $ISI=T$.
Solution profiles in \cref{fig:burst-sols} suggest that the $ISI$s are indeed approximately constant.
Numerically computing $ISI$s for all stable $n:n$ solutions in \cref{fig:bif-diagram} reveals that $ISI$s differ by at most $1\, \si{ms}$ from the intrinsic firing period $T\approx 376\, \si{ms}$.
Assuming $ISI=T$ seems reasonable given that inhibition acting on the silent cell decays exponentially on a much shorter timescale $\tau_{\kappa}$ than the duration of the $ISI$. Therefore, once the silent cell is released its trajectory quickly approaches the spiking limit cycle.
Naturally the above assumption requires a sufficiently small $\tau_{\kappa}$, and fails when $\tau_{\kappa}$ is large.
In the Supplementary Material \cref{sec:tauk} we numerically explore how different values of $\tau_{\kappa}$ affect the $ISIs$ of the active cell.
Finally, assuming $ISI=T$ allows us to ignore the non-linear membrane dynamics during the active phase, and to construct the evolution of the synaptic variables iteratively from spike to spike.
\linelabel{line:E2}

% Assumption 2: Release
\linelabel{line:release1}
Our second assumption states that the silent cell is released and spikes as soon as the total inhibitory conductance $\bar g s$ acting on it drops below some threshold value.
We call this critical threshold value the ``release conductance'', and define it as the value of $\bar g s$ at the time when the voltage of the silent cell first crosses the firing threshold $v_{\theta}$, that is when that cell is released and fires its first spike.
Recall that when a cell is silent its $v$- and $w$-nullclines intersect at a stable fixed point and $\bar g s > g_{bif}$.
% The following does not necessarily imply that it fires instantly on release.
A sufficient condition for the silent cell to be released is therefore $\bar g s < g_{bif}$.
However, depending on the topology of the stable manifold, the $(v,w)$-trajectory of the silent cell can escape the stable fixed point and allow the cell to produce a spike for $\bar g s > g_{bif}$.
In this case the value of the release conductance depends on the type of $n:n$ solution and the coupling strength $\bar g$.
For any stable $n:n$ solution in \cref{fig:bif-diagram} we can compute an associated release conductance numerically by recording the value of $\bar g s$ at the time of the first spike of the silent cell.
% ''Converges'' is probably the wrong word here...
Such values of the release conductance are shown in \cref{fig:gstar-diag}A, and the graph suggests that as $n$ increases, the value of the release conductance converges to some constant conductance value $g^{\star} \approx 0.0068\, \si{mS/cm^2}$.
Here $g^{\star}$ is the value of $\bar g s$ at the end of a cycle of a suppressed solution, just before the active cell spikes.
Using $g^{\star}$ as a constant approximation for the release conductance will allow us to formulate a scalar condition that predicts the release time of the silent cell.
Moreover, using $g^{\star}$ is convenient because its exact value can be derived explicitly, as will be shown in the following section.

Assuming a constant release conductance for all $n:n$ solutions will naturally introduce some error in the prediction of the release time of the silent cell.
We can compute that error for any associated solution in \cref{fig:gstar-diag}A by calculating the time interval between the first spike of the silent cell and the time when $\bar g s$ first crosses $g^{\star}$.
We will call this time interval the ``release delay''.
\Cref{fig:gstar-diag}B shows the numerically computed graph of such release delays.
For $n>1$ the absolute delays are smaller than $2\, \si{ms}$.
Therefore, using
\begin{equation}
	~\label{eq:release}
	\bar g s=g^{\star}
\end{equation}
as a constant release condition for all $n:n$ solutions allows us to accurately predict the timing of the release of the silent cell.
And to simplify the terminology, from now on we will refer to \cref{eq:release} simply as the ``release condition''.
\linelabel{line:release2}

In summary: We assume that the release condition is sufficient to predict when the silent cell is released.
Due to the symmetry of $n:n$ solutions the release occurs at exactly half the period of the full cycle.
The release time therefore uniquely determines the type of $n:n$ solution.
Furthermore, computation of the release time does not depend on the membrane nor the synaptic dynamics of the silent cell.
Instead, the solution of the synaptic variable $s$ of the active cell is sufficient to predict when $\bar g s =g^{\star}$ is satisfied.
\linelabel{line:F}
Finally, the value of $s$ at each spike time is determined by the evolution of the depression variable $d$ of the active cell.
Constructing a solution of $d$ during the active phase of either cell will therefore uniquely determine the solution of the full eight-dimensional network.
However, finding the solution $d$ requires us to know the initial value $d(0)$ at the start of a cycle at $t=0$.
In the next section we will construct a scalar return map that tracks these initial values $d(0)$ from cycle to cycle of stable $n:n$ solutions.

\subsection{Construction of the scalar Poincaré map}
In this section we construct the scalar Poincaré map $\Pi_n:d^{\star}\mapsto d^{\star}$.
Here the discrete variable $d^{\star}$ tracks the values of the continuous depression variable $d$ at the beginning of each $n:n$ burst.
The map $\Pi_{n}$ therefore describes the evolution of $d$, of either of the two cells, from the beginning of one cycle to the beginning of the next cycle.
To simplify the map construction we will assume that an active cell fires exactly $n$ times before it becomes silent.
We will construct $\Pi_n$ by evolving $d$ first during the active phase and then during the silent phase of the $n:n$ limit cycle.
The terms ``active'' and ``silent'' phases will be defined in terms of the state of the depression variable.
During the active phase the depression variable of the active cell both decays and recovers, while during the silent phase it only recovers.
First, let us give explicit definitions of the active and silent phases of a burst.
A schematic illustration of both phases is given in \cref{fig:free-quiet}.

Suppose that at $t=0$ cell 1 becomes active with some initial $d(0)$. Cell 1 then fires $n$ spikes at the uncoupled period $T=T_{a}+T_{s}$.
Let $s(t)$ and $d(t)$ be the corresponding solutions of the synaptic and depression variables of cell 1.
After $n$ spikes the total conductance $\bar g s(t)$ acting on the silent cell 2 has decayed sufficiently to satisfy the release condition~\eqref{eq:release}.
That is at some time $t=(n-1)T + T_{a} + \Delta t$, where $\Delta t < T_{s}$ will be determined below, we have $\bar g s(t)=g^{\star}$ \citep{bose2011}.
Cell 2 is then released and prevents cell 1 from further spiking.
Once released, cell 2 also fires $n$ spikes until cell 1 becomes active once again.
Let $P_n$ denote the full cycle period of a $n:n$ solution:
\begin{equation}
	~\label{eq:P}
	P_n = 2\Big( (n-1)T + T_{a} + \Delta t \Big).
\end{equation}
We can now define the active and silent phases of cell 1 explicitly.
% TODO: This NEEDS editing. Silent phase term here confusing.
The active phase of a burst is the interval that lasts from the first spike time up until the beginning of the silent phase of the last spike, that is for time $0<t<(n-1)T + T_{a}$.
During the active phase of cell 1, the silent cell 2 is inhibited sufficiently strong to prevent it from firing, hence $\bar g s > g^{\star}$.
The silent phase of cell 1 is the remaining duration of the cycle when the cell is not firing, that is for $(n-1)T + T_{a} < t < P_n$.
The silent phase lasts for $(n-1)T + T_{a} + 2\Delta t$.

@@

Given constant $T_{a}$ and $T_{s}$, the derived parameter $\lambda$ determines how much the synapses depresses when $v>v_{\theta}$, while $\rho$ determines how much it recovers when $v<v_{\theta}$.
Since $0<\lambda, \rho<1$, the map in \cref{eq:map-d} is increasing and contracting, with a fixed point at
\begin{equation}
	~\label{eq:dsup}
	d_{s}=\frac{1-\rho}{1-\lambda\rho},
\end{equation}
where $0<d_{s}<1$.
The value $d_{s}$ is the maximum depression value that can be observed in the suppressed solution where the active cell fires at its uncoupled period $T$ (see \cref{fig:burst-sols}E).
Using the release condition in \cref{eq:release} allows us to derive the value of the minimum coupling strength that will produce the full suppressed solution, denoted as $\bar g_{s}$.
Solving \cref{eq:dot-s-down} for $s(t)$ with $t=T_{s}$ and setting the initial value $s(0)=d_s\lambda$ then gives us the aforementioned approximation of the release conductance $g^{\star}$:
\begin{equation}
	\label{eq:gstar}
	\bar g_s d_s\lambda e^{-T_{s}/\tau_\kappa}=g^{\star} \approx 0.0068\, \si{mS/cm^2}.
\end{equation}
By substituting the definition of $d_{s}$ in \eqref{eq:dsup} and rearranging, we can also write $\bar g_s$ as a function of $\lambda$ and $\rho$:
\begin{equation}
	\label{eq:gs}
	\bar g_s(\lambda, \rho) = \frac{1/\lambda-\rho}{1-\rho} e^{T_{s}/\tau_\kappa}g^\star.
\end{equation}
Note that the above dependence of $\bar g_{s}$ on $\lambda$ is linear and monotonically decreasing.
Increasing $\lambda$ reduces the strength of the depression of the active cell.
This in turn allows the active cell to fully suppress the silent cell at smaller values of $\bar g$.

Solving \cref{eq:map-d} gives us the linear map $\delta_n$, that for some initial $d^\star$ computes the depression at the $n$th spike time, that is $d(t_n)$:
\begin{equation}
	\label{eq:delta-map}
	\delta_n(d^\star) = (\lambda \rho)^{n-1} d^\star + (1-\rho)\sum_{i=0}^{n-2}(\lambda \rho)^i.
\end{equation}
Since $\lambda < 1$, function $\delta_n$ is a linearly increasing function of $d^\star$ with a fixed point at $d_s$ for all $n$.
Having identified $d$ after $n$ spikes, we can now use the release condition $\bar g s = g^{\star}$ (\cref{eq:release}) to find $\Delta t$.
At the last ($n$th) spike of the active phase at time $t_n = (n-1)T$ the synapse variable $s$ is set to the respective value of $d(t_n) = \delta_n(d^\star)$, and mirrors the value of $d$ for the duration of $T_{a}$.
At the end of the active phase at time $t_n + T_{a}$ variable $d$ has decayed to $\delta_n(d^\star) \lambda$, therefore
\begin{equation}
	s(t_n + T_{a})=\delta_n(d^\star)\lambda.
\end{equation}
Finally $s$ decays exponentially for $\Delta t < T_{s}$.
Solving \cref{eq:dot-s-down} with initial condition $s(0)=\dn(d^\star)\lambda$ yields:
\begin{equation}
	~\label{eq:s-sol}
	s(\Delta t)=\dn(d^\star) \lambda e^{-\Delta t/\tau_\kappa}.
\end{equation}
Substituting $s(\Delta t)$ into $s$ of the release condition (\cref{eq:release}) gives then
\begin{equation}
	~\label{eq:release2}
	\bar g \dn(d^\star) \lambda e^{-\Delta t/\tau_\kappa}=g^{\star}.
\end{equation}
Our assumption of the release condition guarantees that the silent cell 2 spikes and becomes active when $\bar g s - g^{\star}$ crosses zero.
Solving \cref{eq:release2} for $\Delta t$ allows us to compute $\Delta t$ as a function of $d^{\star}$, which defines the map $F_{n}$:
\begin{equation}
	\label{eq:Fn-map}
	F_n(d^\star):=\tau_\kappa \ln{\left(\frac{\bar g }{g^\star} \lambda \delta_{n}(d^\star)\right)}= \Delta t.
\end{equation}

@@

\Cref{eq:g} also allows us to find the critical fixed point connected with the fold bifurcation, namely $\big(d^\star_b(n), \bar g_b(n)\big)$, which is the global minimum
of $G_n(d^\star_f)$:
\begin{align}
	d^\star_b(n) & = \operatorname{argmin} G_n(d^\star_f), \\
	\bar g_b(n)  & = \min{G_n(d^\star_f)}.
\end{align}
Function $G_n$ is strictly monotonic on the respective intervals of $d^\star_f$ that correspond to the stable and unstable fixed points, that is
\begin{align}
	\dv{G_n}{d^\star_f} & < 0, \text{ for } d^\star_f>d^\star_b(n) \text{ stable},   \\[0.5ex]
	\dv{G_n}{d^\star_f} & > 0, \text{ for } d^\star_f<d^\star_b(n) \text{ unstable},
\end{align}
which allows us to express the stable and unstable fixed points as the inverse of $G_n$ on their respective intervals of $d^\star_f$.
Because we are primarily interested in the stable fixed points $d^\star_f>d^\star_b(n)$, we define the stable fixed point function $d^\star_f = \phi_n(\bar g)$ as
\begin{equation}
	\label{eq:phi}
	\phi_n(\bar g):= G_n^{-1}(\bar g).
\end{equation}
Function $\phi_n(\bar g)$ is also monotonic, and is therefore straightforward to compute numerically.
We use the Python package Pynverse \citep{pynverse} for that purpose.

@@

% TODO: Edit a bit more
\Cref{fig:final-bif} shows the period $P_{n}(\bar g)$ as predicted by the fixed points of $\Pi_{n}$ (\cref{eq:period}) plotted on their respective intervals $\bar g \in [\bar g_{\mathcal{L}}(n),\bar g_{\mathcal{R}}(n)]$ (blue), as well as the cycle period acquired from numerical integration of the full system of ODEs (orange).
Here $g_{\mathcal{L}}(n)$ and $\bar g_{\mathcal{R}}(n)$ were computed from \cref{eq:L,eq:R}, respectively.
Note that the width of $n:n$ branches decreases with $n$, which confirms the inequality in \cref{eq:robustness}.
That is, bursts with more spikes occur on increasingly smaller intervals of $\bar g$, which can be interpreted as a lost of robustness with respect to the coupling strength of long-cyclic solutions.
We also note the occurrence of bistability between pairs of $n:n$ and $(n+1):(n+1)$ branches, which also confirms our initial observation in
\cref{eq:coexistence}.
As previously observed in \cref{fig:folds}B our maps prediction of the cycle period is accurate.
However, the mismatch in the left and right branch borders is significant.
This mismatch might be due to the millisecond release delay error (\cref{fig:gstar-diag}B) induced by our assumption of a constant release conductance for all $n:n$ solutions (see \cref{eq:release}).
Another explanation for the border mismatch could be that our assumptions on the time scales of $(v,w)$ vs $s$- and $d$-dynamics do not hold near the stability borders, and that they can only be captured by more complex approximations.
Nevertheless, our map allows approximate extrapolation of the cycle period and the respective bifurcation borders where numerical integration of the ODEs would require a very small time step.
